\documentclass[12pt, a4paper]{article}
\input{preamble.tex}

\begin{document}

% ── Title page ────────────────────────────────────────────────────────────────
\begin{titlepage}
\centering
\vspace*{3.5cm}
{\fontsize{30}{38}\selectfont\scshape Atmospheric Impact}
\vspace{0.7em}\par

{\large\color{midgray} A Framework for Presence, Expression, and Integrity}

\vspace{2.5cm}

\begin{sidequote}
``Above all else, guard your heart,\\
for everything flows from it.''\\[0.4em]
\normalfont\small\color{midgray} --- Proverbs 4:23
\end{sidequote}

\vfill
{\color{midgray}\small Saint Theocrane}
\end{titlepage}

\tableofcontents
\newpage

% ══════════════════════════════════════════════════════════════════════════════
\section{Core Principle}\label{sec:core_principle}
\input{core_principle.tex}

\section{Operational Summary — Irreducible Form}

Everything in this framework reduces to four conditions.
Not steps. Not tools. Conditions --- without which nothing else operates as described.

% ──────────────────────────────────────────────────────────────────────────────

\subsection{Presence Over Everything}

Feel the room before you act.

Attention must be genuinely outward --- off yourself and onto what is 
actually present. Not what you want to produce. Not what you fear is 
being perceived. What is actually there.

Expression follows from perception. If you are not seeing clearly, 
anything you say will be constructed --- and construction, however 
sophisticated, installs a ceiling. The interaction engages but never 
fully opens.

Presence is not a technique. It is not a state you perform or maintain. 
It is the condition for everything that follows. Without it, the rest 
of this framework is a vocabulary for producing the shape of something 
real without the source.

% ──────────────────────────────────────────────────────────────────────────────

\subsection{The Priority Order}

When you speak, the \hyperref[subsec:priority]{order} is fixed:

\begin{center}
\textbf{Natural State $\rightarrow$ Presence $\rightarrow$ Genuine Origin $\rightarrow$ Non-Interference}
\end{center}

\begin{itemize}
    \item \textbf{\hyperref[sec:natural_state]{Natural State}} --- Are you expressing from 
    your actual temperature, or from a version of 
    yourself the moment seemed to call for?

    \item \textbf{\hyperref[sec:presence]{Presence}} --- Are you actually 
    perceiving what is in front of you, or are you inside your own head?
    
    \item \textbf{\hyperref[subsec:origin_and_closure]{Genuine Origin}} --- 
    Is what you are about to say real? Does it come from something you 
    actually noticed, or from something you want to produce?
    
    \item \textbf{\hyperref[subsec:stopping_point]{Non-Interference}} --- 
    Express the thought at whatever level of closure it actually reached. 
    Do not add what has not arrived. Do not close what has not resolved. 
    Do not leave open what has already closed.
\end{itemize}

Say what is real.\\
Stop where the meaning actually sits.\\
Then leave it there.

This is the whole framework in three lines. Everything else in this 
document is elaboration on why these three fail when any one of them 
is absent --- and what that failure looks like in practice.

% ──────────────────────────────────────────────────────────────────────────────

\subsection{The Calibration Loop}

Presence and genuine origin determine what you express. 
\hyperref[subsec:calibration_loop]{Calibration} determines what you do next.

\begin{center}
\textbf{Observe $\rightarrow$ Express $\rightarrow$ Receive $\rightarrow$ Adjust}
\end{center}

\begin{itemize}
    \item \textbf{Observe} --- Establish baseline before interpreting anything. 
    A signal is only meaningful as a departure from a person's natural register. 
    Read the room before you enter it.

    \item \textbf{Express} --- Use \hyperref[subsec:three_modes]{\textbf{Graze}} 
    as the natural entry: something real, placed lightly, then left. 
    Not pursued. Not explained. Moved past.

    \item \textbf{Receive} --- Read what comes back without projecting. 
    If she moves toward what was placed, 
    \hyperref[subsec:three_modes]{\textbf{Gradual}} is the natural continuation. 
    If she pauses, hold. If she pulls back, reduce.

    \item \textbf{Adjust} --- From what is genuinely present, not from 
    what is desired. Disengagement is information. 
    The correct response is always presence, not pressure.
\end{itemize}

The loop does not have a destination. It runs for as long as the 
interaction runs, and the quality of what it produces is determined 
entirely by whether presence is genuine at every pass through it.

Presence is not a step in the loop. It is the condition in which 
the loop operates at all.

% ──────────────────────────────────────────────────────────────────────────────

\subsection*{Irreducible Core}

If everything above is reduced further --- past the framework, 
past the vocabulary, past the case studies and the failure modes 
and the mechanisms --- three lines remain:

\begin{center}
\emph{Don't rush what is forming.\\
Don't say what the moment hasn't reached.\\
Let her meet you halfway.}
\end{center}

\begin{calloutbox}
Guard the source.\\
Everything that follows flows from it.\\[0.6em]
If you find yourself trying to apply this,\\
you have already left it.
\end{calloutbox}


\section{Natural State}\label{sec:natural_state}

Before presence. Before perception. There is a temperature the man runs at naturally.

Not a mood — moods shift with circumstance. Not a decision — it precedes decision. A stable 
emotional orientation from which everything else arises. For some it is playfulness. For others, 
quiet intensity. For others still, warmth or attentiveness or dry observation. It is not chosen 
in the moment. It is what remains when performance is stripped away and nothing is being managed.

This is the Natural State.

\subsection{The Gap the Framework Could Not Explain}

It matters for one reason the rest of the framework cannot yet explain.

Two men can be equally present. Equally genuine. Equally unforced. One resonates. The other 
lands slightly hollow. The framework, as it stood, could not account for this. Not construction 
— the origin was clean. Not mistiming — the form was correct. Not over-closure — the meaning 
sat where it naturally sat.

The gap was alignment.

\subsection{What Alignment Produces}

When expression matches the Natural State, the receiver feels coherence before content registers. 
Before the words land. Before the meaning resolves. Something in the interaction feels internally 
consistent — like the man in front of her is the same man at every layer. She cannot name what 
she is reading. But she feels it.

This is not the coherence of a man who has simplified himself into something legible. 
It is the coherence of a man who contains more than one thing and has not collapsed any of it.

When expression drifts from it — even toward something also genuine, also unforced — something 
is slightly off. A man whose natural temperature is quiet intensity who reaches for levity he does 
not actually feel. A man who runs warm forcing careful restraint because the framework told him 
to. The words may be true. The perception may be real. The form may be correct.

It still does not resonate.

\subsection{The Constraint}

This is not a call to express everything the Natural State produces. Selection still applies. 
Non-interference still applies. A man reads the room and chooses what the moment can hold.

The constraint is not volume. It is congruence.

What is expressed must not contradict the state it came from. Restraint is not misalignment. 
Performing a different temperature is.

\subsection{Where It Forms}

The Natural State cannot be developed inside interactions. Like the depth the Source Prerequisite 
requires, it forms in the spaces between them --- in whatever the man has lived, survived, and 
stopped pretending about. It is not an asset to deploy. It is simply what is true about him, 
operating beneath everything else.


\subsection{Position in the Framework}

The priority order now reads:

\medskip
\noindent \textit{Natural State $\rightarrow$ Presence $\rightarrow$ Genuine Origin 
$\rightarrow$ Non-Interference}

\medskip
\noindent Natural State is not a step. It is the condition in which all steps operate with 
coherence rather than merely accuracy.

\medskip
\noindent Presence without it produces attentiveness.\\
Presence within it produces resonance.\\
The difference is not visible in the expression.\\
It is felt underneath it.

\subsection{Congruent Expression}\label{subsec:congruent_expression}

Congruent Expression is the condition produced when Natural State,
Presence, and Genuine Origin are all operating without interference.

It has three dimensions.

\textbf{Structural} --- the form of the expression reflects how the
perception formed: layered if layered, incomplete if incomplete, simple
if simple. Without collapse or artificial extension. Most expression
loses this structure automatically. The mind resolves abstract perception
into a transmissible label before speech begins. The effect becomes a
conclusion. \textit{``I like what your smile does to me''} collapses
into \textit{``pretty smile.''} The receiver receives the label. Not
the seeing.

\textbf{Temporal} --- the expression appears when the moment can hold
it, not merely when the feeling first arose. The gap between internal
presence and external expression is not delay for effect. It is the
natural distance between when something becomes real and when the moment
becomes honest enough to carry it.

\textbf{State} --- the register of the expression matches the speaker's
actual emotional temperature. Not the temperature the moment seemed to
call for. His own.

When these three are aligned, the receiver feels coherence before meaning
is processed. When any one breaks, the expression may be understood.
It will not fully resonate.

The collapse is rarely felt by the speaker. A perception resolved into
a label feels complete from the inside --- the loss is structural, and
it appears in the receiver before the speaker can name what went wrong.
This is why congruence cannot be produced by intention alone. It requires
the self-awareness to catch the collapse before it happens --- to stay
with the effect long enough that it reaches expression without being
converted into something easier to say.

\medskip
\noindent Congruence is not a technique within verbal presence.\\
It is the condition that makes verbal presence honest at all.

% ══════════════════════════════════════════════════════════════════════════════
\section{Presence}\label{sec:presence}
\input{presence.tex}
% ══════════════════════════════════════════════════════════════════════════════

% ══════════════════════════════════════════════════════════════════════════════
\section{Verbal Presence}\label{sec:verbal_presence}

Everything in verbal expression reduces to three movements.
Not steps. Not tools. Movements --- without which nothing said
operates as described.

\begin{center}
\emph{Something real formed. Find it.\\
Choose what belongs to this moment.\\
Say it at the temperature it came from. Then stop.}
\end{center}

\begin{calloutbox}
Resonance does not look like pondering.\\
It looks like realness. And non-interference.\\[0.6em]
If you find yourself polishing,\\
you have already left the thought.
\end{calloutbox}

% ──────────────────────────────────────────────────────────────────────────────

\subsection{Something Real Formed}

Before the words. Before selection. Before release.

Something genuine was noticed --- not a label, not a verdict, but the
raw shape of what was actually there. Less \textit{``you're pretty''} and
more \textit{``the way you look today\ldots it stands out to me.''}
The difference is not politeness or style. One has already been collapsed
into a conclusion. The other is still carrying the shape of what was
noticed. The moment a perception resolves into a label before it is spoken,
the receiver receives the label. Not the seeing. The mechanism behind
this collapse, and what it costs, is named in
\hyperref[subsec:congruent_expression]{Congruent Expression}.

This is not something to produce. It is the condition that
\hyperref[sec:presence]{Presence}, operating genuinely, already provides.
If something real has not formed, nothing in what follows repairs that.

This is also where the \hyperref[sec:expression_origin]{Expression Model}
begins. A thought that has not yet resolved into closed meaning ---
genuinely, not strategically --- is already
\hyperref[sec:expression_origin]{Genuine~$+$~Open} before it has been
spoken. Verbal presence is what keeps it there on the way out.

% ──────────────────────────────────────────────────────────────────────────────

\subsection{Selection}

Of the several things forming --- reflex, reaction, coherence, noise ---
selection is the quiet judgment of which one belongs to this moment
and this person.

It is the only conscious movement in the sequence. And even then, barely.
It is not deliberate in the way planning is. It does not run through
options. It feels which of the things forming is actually true right now
--- and whether this moment can hold it.

Multiple perceptions may arise simultaneously --- each genuine, each
partial, each competing. Selection among them is not planning. It is
the felt sense of which fragment is least resolved, least labelled, most
alive in this moment. That requires a quality of self-awareness distinct
from anything else in this framework: the ability to hold several
half-formed things at once without collapsing them into whichever one
is easiest to say.

\begin{center}
\textbf{Selection asks: does this moment call for this?}
\end{center}

Not the most impressive. Not the safest. Not the one most likely to land.
The one that is real.

A man who selects carefully from genuine perception is not constructing.
He is reading what the room can hold and choosing whether to place
something in it. This is the distinction between selection and
interference, named fully in
\hyperref[subsec:selection_and_interference]{Selection and Interference}:
selection is upstream and outward --- a genuine reading of the moment.
Interference is downstream and inward --- management disguised as care.

Selection also determines which mode of
\hyperref[sec:generative_incompletion]{Generative Incompletion} the
expression enters. A graze is selected when the thought is real but the
moment calls for lightness. Gradual is not selected at all --- it
unfolds as the shared field deepens. Fracture bypasses selection
entirely: it is what happens when something real exceeds containment
before selection could operate.


\subsection{Formation Awareness}

Before selection. Before release. There is a window --- brief, rarely noticed — in which the thought is still arriving.

It has texture at this stage. Not yet a sentence. Not yet transmissible. It may be layered, partially contradictory, unresolved at its edges. 
This is not a problem to fix. It is the material. What the framework asks you to preserve is not the polished form --- it is this: the thought 
as it actually arrived, before the mind began converting it into something easier to carry.

The collapse happens here. Not at release. Not at selection. In this window, before either has operated, the mind reaches --- almost automatically --- toward resolution. 
A cleaner word. A simpler shape. The version that will land without friction. The reach feels like clarity. It is not. It is the first interference.

\textbf{What polishing feels like from the inside:}

A slight pull toward a more familiar word. The urge to resolve what is still open. The sense that the thought needs one more step before it is ready. 
The instinct to make it safe enough to say. These are not signs that the thought is still forming. They are signs that the mind has already decided the 
thought needs to be better than it is.

\textbf{The discipline is not: do not polish.}

It is: notice the reach before it completes.

Polishing that is caught mid-motion can be released. Polishing that completes before it is noticed becomes the expression --- 
and from the inside, it feels identical to the real thing. This is why the collapse is rarely felt by the speaker. The smoothed version arrives at the surface 
already wearing the shape of something genuine. The only way to catch it is to be watching earlier than most people think to watch.

This is not a technique that can be applied at the moment of speaking. It is a quality of attention that has to be present before the thought surfaces --- 
already watching, already waiting to feel the reach. Without it, non-interference has no instrument. The man knows he is not supposed to polish. 
He does not know he already has.

% ──────────────────────────────────────────────────────────────────────────────

\subsection{Release}

Say it at whatever level of closure it reached. Not elevated to sound
more significant. Not softened to sound safer. At the register it arrived
in --- because that register is part of the meaning.

The risk of polishing is that polishing is, by its nature, construction.
The shift from genuine to constructed does not occur in expression, but in position.
The moment you become aware of the thought as something to improve, you have already left it.
You refine something to land better, to produce a cleaner effect --- and
by any effect produced, that construction negates itself. The receiver
does not feel the thought. They feel the attempt.

\begin{center}
\textbf{Interference asks: how do I improve what is already here?}
\end{center}

So say it. Stop where it stopped. Leave it at the temperature it came
from. The man who has not gotten in the way of it is the only one whose
words carry what he actually meant.

This is where verbal presence connects directly to
\hyperref[sec:co_authorship]{Co-Authorship}. When a thought is released
at its natural edge --- not over-completed, not softened back into
safety --- the receiver is handed something unfinished. Her mind moves
automatically to complete it. The meaning she generates comes from
inside her. She does not receive it. She builds it. That is the
\hyperref[subsec:completion_bond]{Completion Bond} forming: not through
what was delivered, but through what she was invited to finish.

Over-completion does not just fail to produce co-authorship. It
collapses it. When meaning that has just landed is explained,
elaborated, or softened, the space in which she was still completing it
is filled from outside. She was mid-construction. The construction is
finished for her. The reaching stops.

Release at the natural edge. Then leave it where it sits.

% ──────────────────────────────────────────────────────────────────────────────

\subsection{What Verbal Presence Is Not}

Verbal presence is not silence. Silence is verbal presence when nothing
has formed. It is avoidance when something has. The distinction matters
because performing silence is its own form of construction --- it
produces the shape of weight without the source.

Verbal presence is not speed. A thought released quickly from genuine
perception is verbal presence. A thought held and polished and then
released slowly is not. The variable is not pace. It is whether the
expression was interfered with between formation and release.

Verbal presence is not mindlessness. The discipline of selection is
still operating. What is absent is not judgment --- it is management.
The man is still reading the room, still feeling what the moment can
hold. He is simply not reaching back into the thought once it has
formed to improve it.

What verbal presence is not, most precisely: it is not the absence of
care. It is care directed entirely outward --- at the person and the
moment --- rather than inward at the expression itself.

% ──────────────────────────────────────────────────────────────────────────────

\subsection*{Irreducible Core}

If the three movements above are reduced further --- past the
distinctions, past the examples, past the failure modes --- three lines
remain:

\begin{center}
\emph{Something real formed. Find it.\\
Choose what belongs to this moment.\\
Say it at the temperature it came from. Then stop.}
\end{center}

\begin{calloutbox}
Resonance does not look like pondering.\\
It looks like realness. And non-interference.\\[0.6em]
If you find yourself polishing,\\
you have already left the thought.
\end{calloutbox}

% ══════════════════════════════════════════════════════════════════════════════
\section{The Expression Model --- Origin and Meaning Closure}\label{sec:expression_origin}
\input{expression_model.tex}
% ══════════════════════════════════════════════════════════════════════════════
\section{Generative Incompletion}\label{sec:generative_incompletion}
\input{GenerativeIncompletion/main.tex}
% ══════════════════════════════════════════════════════════════════════════════
\section{Co-Authorship}\label{sec:co_authorship}
\input{CoAuthorship/main.tex}
% ══════════════════════════════════════════════════════════════════════════════
\section{Reception and Calibration}

The man who transmits without receiving is not present. He is performing. Every element of 
expression described in the preceding sections depends on what comes back being read 
accurately and responded to honestly.

\subsection{Baseline First}\label{subsec:baseline}

Before any signal can be read, baseline must be established. 
A signal is only meaningful as a departure from a person's natural register. 
Reading without baseline is projection: you are seeing what you want to see, not 
what is there.

The first moments of any interaction should be genuinely observational --- not transmitting, 
not planning. Just watching. Learning the register before attempting to read the deviation.

\subsection{Stages of Engagement}

Engagement does not move in clean steps. It breathes --- advancing and receding. 
The stages below are reference points, not a sequence to execute.

\input{stages_of_engagement.tex}
\subsection{Disengagement}

Not every interaction moves forward. Disengagement signals --- scanning the room, 
shortening her answers, leaning away, laughter that sounds performed --- are information, 
not failure. The correct response is always reduction: less output, more presence, return 
to baseline observation.

\begin{calloutbox}
Disengagement is information.\\
The correct response is presence, not pressure.\\
A man who reads accurately must be willing to read what he does not want to see.
\end{calloutbox}

\subsection{Graze, Gradual, and Calibration}

Of the three modes, Graze is the most calibrated. Because it releases 
something real at low intensity, moves on, and does not extend, what 
comes back is uncontaminated --- the receiver had no pressure to 
respond to, so whatever she does next is entirely hers. That is pure 
signal.

Graze is not just the lightest form of expression. It is the most 
diagnostic. Not because it is easy, but because it does not rely on 
buildup, escalation, or timing. Something real is noticed, lightly 
named, and left where it lands --- and then the moment continues. 
No extension. No clarification. No pursuit. No lingering. The space 
remains clear because he already moved on.

Gradual works hand in hand with Graze precisely because of this. 
A Graze enters the space and passes through. What the receiver does 
with it determines whether Gradual begins at all. If she moves toward 
it --- however slightly --- Gradual is the natural continuation: the 
guard softening incrementally, what is real becoming less contained 
over time. Graze opens the door. Gradual continues only because she 
chose to walk through it.

Fracture is different in kind. It is not calibrated. It does not read 
the room and respond --- it breaks through before reading was possible. 
But this is precisely the source of its power. The receiver does not 
experience it as something aimed at her. She experiences something real 
exceeding containment, which is the one signal that cannot be 
constructed. Graze and Gradual can be imitated structurally. Fracture 
cannot --- because the moment you decide to fracture, you have already 
closed yourself.

The three modes are not interchangeable tools. Graze is the entry. 
Gradual is the unfolding. Fracture is what happens when something real 
has grown too present to hold. Calibration governs the first two. 
The third is beyond it --- and that is why it lands.

\subsection{Three Pressure States}
\input{pressure_states.tex}

\subsection{What Pressure Reveals}

Genuine expression does not break under intelligent pressure. It deepens. When a receiver 
pushes back --- naming the mechanism, calling out the vagueness, demanding 
specificity --- she is not threatening the framework. She is revealing whether it has a 
real foundation.

Constructed expression breaks under this pressure because pressure exposes architecture. 
Genuine expression has no architecture to expose. When she pushes and finds 
something real --- honest uncertainty, unfinished thought, actual vulnerability --- the 
pressure becomes confirmation rather than threat.

The framework does not protect you from being seen. It only functions for a man for 
whom being seen is not a threat.

\subsection{Respect Their Pacing}

When someone pauses, softens, or pulls back from something they were beginning to say --- they 
are not failing to communicate. They are telling you where the boundary of their comfort 
currently sits. The instinct is to call it out, to invite them in, to name what 
you noticed and ask them to open further. 

\textbf{DO NOT.}

Naming what someone held back does not create safety. It creates exposure. They did not 
choose to open that far yet, and pointing at the threshold does not move it --- it makes 
the threshold visible and watched, which is precisely the condition that keeps it closed. 
Safety creates revelation. Pressure kills it, even well-intentioned pressure. The refinement 
is not \textit{don't call it out} but \textit{respect their pacing unless they invite you in}. 
When she opens on her own, she owns the opening. When she opens because you beckoned, she is 
performing it.

\subsection{Calibration}\label{subsec:calibration}

The loop is simple: feel the room, speak from something real, read what comes back without 
projecting, adjust from what is genuinely present rather than from what is desired, and 
begin again. Presence is not a step in the loop. It is the condition in which the loop 
operates at all.

% ── 6.9 The Calibration Loop ─────────────────────────────────────────────

\subsection{The Calibration Loop}\label{subsec:calibration_loop}
\input{calibration_loop.tex}

% ══════════════════════════════════════════════════════════════════════════════
\section{Failure Modes}

The framework fails in predictable ways. Each failure has the same root: 
the form is present but the origin is wrong.

\input{failure_modes.tex}

\begin{calloutbox}
The question is never how open the expression is.\\
The question is whether the openness was native to the thought\\
or applied to it afterward.\\[0.4em]
One is presence. The other is craft pretending to be presence.
\end{calloutbox}

% ══════════════════════════════════════════════════════════════════════════════
\section{Ethical Boundary}

The framework describes how genuine presence and honest expression affect another person. 
That description creates responsibility.

Reading someone accurately is not permission to direct them. Seeing her signals, 
her openings, her hesitations --- the clearer you see, the more carefully you must move.

\begin{calloutbox}
The goal is not to trap attention.\\
The goal is not to produce a predetermined outcome.\\
The interaction should remain non-coercive at every stage.\\
She retains full agency throughout.
\end{calloutbox}

The moral test is simple. Could you switch, at any point, to warm and 
direct communication --- dropping all craft and simply being honest with her about what 
you are noticing? If yes, the framework is in service of connection. If no, the expression 
has become engineered and the source has been corrupted.

There is a distinction between \term{guarding} and \term{hiding}. Guarding is selective 
revelation in service of something real --- the guard is present because something worth 
protecting is behind it. Hiding is using openness as a mechanism for control. Both look 
like restraint from the outside. The man operating the framework knows which one 
he is doing. Hiding uses open meaning as self-protection or manufactured mystery. 
Guarding uses open meaning because the thought genuinely has not resolved yet. The framework 
only functions honestly from the guarding position.

\subsection{The Source Prerequisite}

The framework functions only when the source is genuinely deep. This is not a moral 
instruction. It is a functional description.

Generative Incompletion only produces the Completion Bond when what escapes is genuinely 
real. A man who performs the pauses and trails the sentences without something true behind 
them produces nothing worth completing. She will feel the hollow underneath --- not always 
consciously, not always immediately --- but eventually, and retroactively.

The depth required cannot be developed inside interactions. It develops in the spaces between 
them --- in the pain that taught you to stop aiming for outcomes, in the regret that taught 
you what presence actually costs, in the quiet that showed you the difference between a moment 
you made and a moment you were in. It also forms in the habit of noticing your own 
perception before it resolves --- of sitting with what an experience produces in you before
the mind converts it into a label. A man who never does this has no
unconverted material to express.

Two words without elaboration, said in an honest moment, carry more weight than any 
crafted sequence of fragments. Because they came from somewhere real.

The same holds for complexity. A man who contains more than one truth and releases it 
without collapsing it first is not performing depth. He is being accurate. 
Flattening the state into something easier to express is its own distortion — quieter than 
construction, but the same in kind.

If everything in this framework were compressed to its irreducible core, it would be 
three lines. Don't rush what is already forming. Don't say what the moment hasn't reached. 
Let the other person meet you halfway.

The depth the Source Prerequisite describes is what the \hyperref[sec:natural_state]{Natural State} draws from. 
They are not the same thing — the Source is what has been lived; the \hyperref[sec:natural_state]{Natural State} is 
how that living has organized itself 
into a consistent orientation. One is history. The other is character.

\begin{calloutbox}
Guard the source. Everything that follows flows from it.
\end{calloutbox}

% ══════════════════════════════════════════════════════════════════════════════
\section{Case Studies}\label{sec:case_studies}
\input{CaseStudies/main.tex}
\end{document}