Every expression has two properties: where it came from, and whether 
the meaning resolved before it was released. These two variables produce 
the structure of the entire framework.

\subsection{The Two Axes}\label{subsec:origin_and_closure}

Every expression has an \term{origin} and a \term{meaning closure}.

\textbf{Origin} describes whether the expression is grounded in 
genuine perception --- something the speaker actually felt or noticed --- or 
constructed for effect without a real internal anchor. This is the axis that 
cannot be faked over time. The receiver's nervous system is calibrated to detect 
construction even when the conscious mind cannot name it.

\textbf{Meaning Closure} describes whether the meaning resolved before expression, 
or whether the receiver must complete it on their own. This is not about whether the 
sentence grammatically finished. A sentence can close syntactically and still 
leave meaning entirely open. The axis measures whether what was \textit{meant} 
resolved --- not whether the words did.

\subsection{The Four Positions}

\textbf{Constructed + Closed.} Expression with no genuine feeling at origin. The 
thought is formed, the meaning is delivered, nothing is left. This is the only 
position the framework treats as a clean failure mode. It produces a subtle audit 
in the receiver --- they sense the machinery even if they cannot name it. Over time, 
sensed engineering creates retroactive resistance: prior moments get re-examined and 
recontextualised.

\textbf{Genuine + Closed.} Genuine perception at origin. The meaning resolves fully 
before expression. The speaker chooses what to reveal and how. Craft serves truth. 
This is the baseline of the framework --- honest, shapeable, sustainable. Not a 
lesser mode. Often the right one.

\textbf{Constructed + Open.} The blur. A thought that completed internally, then had 
its meaning obscured deliberately --- softened, trailed, made to seem unfinished. 
The receiver receives initial intrigue but when clarity arrives the investment drops: 
nothing was built, something was only clarified. This is constructed ambiguity by 
softening, and it is the failure mode most easily confused with the next position.

\textbf{Genuine + Open.} Genuine perception at origin. The meaning is not resolved 
for the receiver --- either because the thought genuinely had not finished forming, 
or because the sentence closed but the implication was withheld before it could land. 
The receiver must complete the meaning themself. This is the operative quadrant of 
the framework. It is the condition that produces co-authorship, investment, and the 
Completion Bond. 
\term{Cognition Fracture} is the strongest expression of this 
position: meaning so open that the thought broke before it could form at all, 
escaping involuntarily. It is not a separate quadrant --- it is the far end of 
Genuine + Open, where incompletion is at its most involuntary and therefore most 
indefensible.

\subsection{The Spectrum}

\begin{center}
\small\color{midgray}
\textbf{Constructed + Closed} $\longrightarrow$ \textbf{Genuine + Closed} $\longrightarrow$ \textbf{Genuine + Open} $\longrightarrow$ \textbf{Cognition Fracture}\\[0.4em]
engineered, delivered \hspace{0.4cm} honest craft \hspace{0.6cm} meaning open, receiver completes \hspace{0.3cm} involuntary release
\end{center}

\begin{calloutbox}
The key variable is not how polished the expression is.\\
It is whether the origin is real.\\[0.6em]
A sentence may close grammatically and still belong to Genuine + Open\\
if the meaning did not resolve for the receiver.\\
``Our eyes met'' is syntactically complete. The meaning --- why it matters,\\
what it means that you came over --- is entirely open. They fill it.\\[0.4em]
The axis measures whether the meaning resolved. Not whether the sentence did.
\end{calloutbox}

\subsection{The Priority Order}\label{subsec:priority}

The framework does not advocate for maximum openness. It is not a system for 
producing Genuine + Open on demand. The correct operating sequence is simpler and 
more demanding than any technique.

\textbf{0. Natural State.} Before presence, before expression — what temperature 
do you actually run at? Everything must stem from this. Not a mood. Not a decision. 
The stable orientation from which coherent expression becomes possible at all.

\textbf{1. Presence.} Be genuinely outward. Without this, nothing else in the 
framework operates.

\textbf{2. Genuine Origin.} Say what is real. If the origin is not genuine, 
the quadrant does not matter.

\textbf{3. Non-interference.} Express the thought at whatever level of closure it 
actually reached. Do not add meaning that had not arrived. Do not close meaning 
that had not resolved.

\vspace{0.5em}

Non-interference does not require total expression. It does not mean externalising 
the full internal state. It requires that what is expressed remains unaltered at its 
origin.

What is withheld is not distortion. What is altered is.

A man may feel more than the moment can hold. What he releases may be partial — but 
it must be clean.

The constraint is not volume. The constraint is truth.

\vspace{0.5em}

The practical implication: if a genuine thought resolves into closed meaning, 
deliver it closed. Genuine + Closed is not a failure. If a genuine thought leaves 
meaning open, let it land open. Do not reach back and complete what the moment 
did not complete.

The discipline is non-interference with wherever the meaning naturally sits.

\subsection{Why Constructed Expression Fails Over Time}

The receiver's nervous system detects constructed expression before the conscious 
mind names it. The response is not immediate rejection. It is the quiet installation 
of a ceiling --- they engage, but never fully opens.

When the engineering is eventually confirmed, and it tends to be, the damage is 
retroactive: prior moments get recontextualised. Everything that landed before 
gets re-examined through the lens of the machinery that was eventually found.

Honest expression does not produce this ceiling. It allows the interaction to 
deepen without a floor beneath it.
