\subsection{Vagueness Mistaken for Depth}

Open meaning without genuine anchor becomes blur. The speaker releases fragments 
because they sound interesting, not because something real was still forming. 
The receiver cannot complete a fragment that was never started. They interprets 
it as evasion and pulls back.

\subsection{Constructed Ambiguity by Softening}

A thought completes internally. The speaker knows what he means. He softens the 
delivery --- trailing it, blurring the edges --- so it reads as open rather than closed. 
The receiver receives intrigue. When the meaning eventually resolves, 
the investment drops: nothing was built, something was only clarified. The difference between 
this and Generative Incompletion is invisible from outside. It is the difference between 
meaning that genuinely had not resolved and meaning that had resolved and was then obscured.

\subsection{Avoidance Disguised as Openness}

A man can use leaving space to avoid being direct when directness is called for. 
When the receiver invites grounding --- when they open a door and waits --- continued 
incompletion is no longer Generative Incompletion. It is avoidance with better vocabulary. 
They will name it eventually, even if they cannot name it precisely.

\subsection{Overuse of Incompletion}

Sustained open meaning, used indiscriminately, stops reading as unfinished thought and 
starts reading as a pattern. The receiver adjusts their baseline. What once produced curiosity 
now produces mild irritation: ``he keeps almost saying something.'' Genuine + Closed expression 
is not a lesser mode. It is often the right one.

\subsection{Incompletion Without Grounding}

The most common failure: using the structure without the origin. Performing pauses. 
Trailing sentences for effect. The receiver's nervous system is calibrated to detect 
the difference between a man revealing something true and a man performing the shape of 
revelation.

\subsection{The Cold Start Failure}

Generative Incompletion requires presence as its soil. Without an established 
baseline --- without the room being felt first, without genuine outward attention --- an open 
line lands as strange rather than unfinished. The case studies in 
\hyperref[sec:case_studies]{Case Studies} worked because the atmosphere was 
already held before the first incomplete thought was released. 
Presence is not optional preparation. It is the condition without which nothing else 
operates as described.

\subsection{Turning Observations Into Rules}

The most insidious failure mode is not misapplying the framework. It is internalising its 
observations as instructions. A man who reads this document and extracts 
rules --- \textit{be silent more, don't call things out, hesitate intentionally} --- has 
converted description into technique. He is now constructing the shape of what the 
framework describes rather than inhabiting the source it requires.

The warning is precise: the moment you find yourself performing silence, 
manufacturing hesitation, or strategically withholding completion, you have left 
Genuine + Open and entered Constructed + Open. The structure is identical. 
The origin is wrong. They will feel the hollow underneath it, not always immediately, 
but eventually --- and retroactively.

Read the framework to understand the mechanism. Do not use it to generate behaviour.

\subsection{Register Blindness}

A man can operate with genuine origin, correct form, and honest incompletion --- and still fail, because he did not notice that the moment had shifted into something that was not asking for openness at all.

When the other person offers something deliberate --- a careful question, a real admission, something that required genuine presence to form --- the honest response is not a fragment. It is reception. Sitting with what was offered. Coming back with something equally considered.

Continued openness in that moment is not depth. It is the man applying his usual instrument to a moment that needed a different one. She asked something real and was handed something that made her complete the meaning herself, when what she needed was a man who actually received what she said.

This failure looks like presence from outside. The origin is clean. The form is correct. But the mode does not match what the room became. Presence that cannot shift registers when the interaction shifts is presence running on pattern, not perception.

\textbf{The correction is not a technique}. It is noticing. When the moment asks for arrival --- for weight, for a full answer, for a man who sat with the question --- arrive. Genuine~+~Closed at the right moment is not a concession. It is what presence produces when what is needed is not invitation but answer.

\subsection{Misalignment Disguised as Genuine Expression}
The most invisible failure mode. Origin is clean. Form is correct. 
Timing is sound. But the expression contradicts the man's natural temperature — warmth performed 
by someone who runs cool, levity forced by someone whose depth is the real thing. The receiver 
does not experience this as construction. She experiences it as something slightly inconsistent. 
She cannot name it. It accumulates quietly until the interaction feels subtly unreliable 
without her knowing why.