
\vspace{0.5em}
\textbf{Neutral} --- No signal that the interaction has registered as significant. 
The correct move is almost nothing: presence, baseline observation, low output.

\vspace{0.5em}
\textbf{Curiosity} --- Something has registered. Attention has oriented. 
Signals are subtle: a glance held slightly longer than necessary, a listening posture, 
a smile that arrives before they decided to produce it. Curiosity is fragile. The primary 
driver is perceived authenticity --- the sense that what is happening is unrehearsed.

\vspace{0.5em}
\textbf{Guard Drop} --- The nervous system shifts from threat detection toward 
social engagement. This shows up involuntarily --- a relaxation in posture, 
breathing that slows, a physical ease that was not present before. It cannot be forced. 
It is produced by the absence of pressure more than by the presence of charm.

\vspace{0.5em}
\textbf{Synchrony} --- The receiver begins producing their own incomplete thoughts, their own hesitations, 
their own unguarded moments. They are not mirroring consciously. The shared field has deepened 
to the point where their expression is being drawn out by the atmosphere, not delivered to it.

\vspace{0.5em}
\textbf{The First Slip} --- Their first involuntary signal directed at you, not simply produced 
in your presence. A laugh that surprised them. A comment they did not plan to make. Eye contact 
held past comfortable(in case of romantic contexts). They are now fracturing in the same way.

\vspace{0.5em}
\textbf{Bilateral Moment} --- The first voluntary contribution to the shared atmosphere. 
They finish a thought you left open. They creat a pause themself. They tease(once again, can vary in terms of contex). 
At this point, they are no longer a receiver of atmosphere. They are co-authoring it.
