When meaning is built mutually, the investment it produces is different 
in kind from anything delivered complete. A meaning that arrived from 
outside can be held at a distance, examined, agreed with or rejected. 
A meaning that was built from inside cannot. It carries the builder's 
own material. They cannot be indifferent to what they made.

This is the Completion Bond: not an attachment to the other person, 
but an attachment to the meaning itself --- and through it, to the 
interaction that made the meaning possible. It does not require 
intensity to form. It requires only that the meaning was genuinely 
incomplete before they moved toward it, and that they moved of their own 
volition.

What distinguishes it from ordinary interest is its durability. 
Interest produced by delivered meaning closes when the meaning is 
fully received. The Completion Bond does not close --- because the 
meaning was never fully delivered from outside. They wrote part of it. 
That part stays with them, because it came from them.

This also explains the reciprocal disclosure it tends to produce. 
When meaning has been built mutually, the psychological position 
of both people shifts. Neither was operating on the other. Neither 
was the target of a move. Something real was built in shared space, 
and the nervous system of each person reads the other as safe --- 
not because trust was established through disclosure, but because 
the interaction itself was not coercive. Her guard does not lower 
as a decision. It lowers as a consequence.

\begin{calloutbox}
Delivered meaning produces a receiver.\\
Built meaning produces a participant.\\[0.4em]
The receiver can walk away from what they were given.\\
The participant carries what they helped make.
\end{calloutbox}