\input{CoAuthorship/intro.tex}
\subsection{The Completion Bond}
\input{CoAuthorship/completion_bond.tex}
\subsection{Let Her Move Toward You}

Co-authorship cannot be forced. The man who presses for completion --- 
who crowds the space before the receiver has had time to fill it --- does not accelerate 
the mechanism. He replaces it. What arrives under pressure is compliance, 
not investment. They moved because the space closed, not because they chose to enter it.

The Completion Bond forms only when they move on their own terms. 
What they reache voluntarily is theirs. What they are directed towards is not. 
The distinction is not subtle --- it determines whether the meaning they 
carry after the interaction belongs to them or to the interaction itself.

This is why restraint is not a stylistic preference in this framework. 
It is a structural requirement. The space in which they completes the meaning 
must remain genuinely open --- not performed open, not strategically open, 
but open because the speaker did not reach past the natural edge of what had formed.

\begin{calloutbox}
Assertion delivers meaning complete.\\
Co-authorship leaves meaning open at the edge where it genuinely sits.\\[0.4em]
One produces a receiver. The other produces a participant.\\
Participation cannot be forced. It can only be made possible.
\end{calloutbox}

\subsection{The Collapse Condition}

The Completion Bond does not only fail to form. It collapses --- 
quietly, without announcement --- when the conditions that produced 
it are reversed.

The reversal does not require hostility or error. It requires only 
that one person begins resolving meaning before the other has finished 
building it. The shared space closes. What was mutual becomes directed. 
The interaction has not ended, but co-authorship has.

This happens in recognisable ways.

When meaning that has just landed is explained --- elaborated, softened, 
clarified --- the space in which they was still completing it is filled 
from outside. They was mid-construction. The construction is finished 
for them. What they were reaching towards, building, becomes something they were handed. 
The reaching stops.

When what they completed is named --- reflected back, confirmed, 
labelled --- the meaning moves from the shared space into explicit 
territory. It becomes an object between two people rather than 
something alive in the space they are both inside. It cannot be 
returned to what it was. The intimacy of built meaning depends on 
it remaining partially unspoken, even after it has been felt by both.

When one person begins moving before the other has finished --- 
pressing the next fragment, closing the distance, advancing the 
interaction --- the other person's motion converts from voluntary 
to reactive. They were choosing to move. They are now responding to 
pressure. These feel similar from the outside. They are not the 
same from the inside. The Completion Bond requires that both people 
remain genuinely free to stop. The moment that ceases to be true, 
what is forming is no longer co-authorship.

\begin{calloutbox}
The bond does not break dramatically.\\
It stops being real.\\[0.4em]
Explain after it lands --- they stops building.\\
Name what was built --- it becomes an object.\\
Move before the receiver finishes --- they stop choosing.\\[0.4em]
Co-authorship requires that both people\\
remain free to stop at any moment.\\
That freedom is not a courtesy.\\
It is the condition.
\end{calloutbox}