\textit{Setting: A low concrete wall along a park walkway, early evening. 
Soft warm streetlights. A light breeze. She sits scrolling through her phone --- 
not fully present in it, just occupying herself. Glances up briefly when he sits, 
then back down. This exchange answers a different question from the others: 
not what the framework looks like when conditions are neutral, but whether it 
holds when the person across from you is guarded, observant, and actively 
checking whether what she is receiving is real.}

\goldrule

\speaker{Him}{sits next to her; soft tone; no setup}
{hey.}
{Plain entry. No line, no craft. She tests the opener immediately --- 
checking for pattern or presence. He offers neither defense nor explanation.}

\speaker{Her}{glances up; a pause --- deciding whether to engage; then a small nod; 
eyes flick to his smile, then ahead}
{\ldots hey. you just\ldots say hey to random people or?}
{The first check. She is reading the texture of the opener --- 
was this a line, or did something real produce it? The question is not hostile. 
It is precise.}

\thinrule

\speaker{Him}{laughs a little}
{not always.}
{\textbf{Genuine + Closed. Two words. The contradiction is real and unresolved --- 
``not always'' implies a condition without naming it. She does not disengage. 
She leans in: ``so why me then?'' Her attention has oriented. 
She was watching for performance; plain honesty passed straight through her.}}

\speaker{Her}{head tilts; pressing}
{so why me then?}
{She is not checking mechanically. She actually wants to know if there is a real 
reason. The distinction matters to her.}

\thinrule

\speaker{Him}{warm eye contact}
{you caught my attention.}
{She presses immediately: ``that's a bit vague.'' She detected vagueness on 
schedule and named it directly.}

\speaker{Her}{direct; not hostile --- probing}
{that's a bit vague.}
{She is checking for construction. Constructed expression would elaborate here. 
Genuine origin does not.}

\thinrule

\speaker{Him}{leans back; giving her space}
{it means I noticed you and felt like starting a chat.}
{\textbf{Genuine + Closed. She registers the lean back --- the physical 
non-pressure --- before she processes the words. Her shoulders ease. 
``that's\ldots more normal.'' The first micro-softening. She had been braced 
for a line. She received an observation and a body that did not crowd her. 
She had nothing to pull back from.}}

\speaker{Her}{shoulders easing; something quieter entering her voice}
{that's\ldots more normal.}
{First micro-softening. The guard has not dropped --- but it is no longer 
fully raised. She has placed him outside the category she was bracing for.}

\thinrule

\speakeraction{Him and Her}{several exchanges of light challenge and plain response 
follow; each time she checks for performance, urgency, or vagueness, she finds 
honest incompletion or grounded directness in its place; she finds nothing to 
push against}
{\textbf{By the time she asks ``what made it feel right right now?'' her tone 
has shifted from checking to genuine inquiry. She is no longer running an audit. 
She is curious about the answer.}}

\speaker{Him}{smiles; then pauses mid-thought; searching for the words before 
releasing them}
{always. when I feel like\ldots I might later wonder, I go for it.}
{\textbf{Generative Incompletion, gradual. The pause before ``I might later 
wonder'' is not performed. The thought arrived ahead of articulation. She watches 
the pause --- that part lands more than the words themselves. ``most people 
just\ldots overthink it and move on.'' She is beginning to place him against a 
contrast class. The guard is softening, not because he pressed it, but because 
he has given it nothing to hold against.}}

\thinrule

\speaker{Him}{}
{whether I'll mess up, look stupid, or things like that.}
{\textbf{Genuine + Closed. She goes quiet for a beat. ``yeah\ldots that part's 
real.'' Said almost to herself. This is the first moment she stops directing 
speech at him and begins thinking alongside him. The shared field has begun 
forming.}}

\speaker{Her}{almost to herself; not performing the thought}
{yeah\ldots that part's real.}
{She is no longer directing words at him. She is thinking alongside him. 
The shared field has begun.}

\thinrule

\speaker{Her}{after he asks why she raises the question}
{\ldots no big reason. \textit{shrugs lightly} just trying to see if you 
actually do what you're saying or if it's just\ldots nice phrasing.}
{This is the clearest statement of what she has been doing in plain language: 
she is checking for construction. What follows is the framework's core test. 
Constructed expression breaks here. Genuine origin has nothing to hide.}

\speaker{Him}{a bit more tender; not overtly}
{can I be honest?}
{}

\speaker{Her}{small shrug}
{\ldots you can. doesn't mean I'll agree though.}
{}

\speaker{Him}{}
{sometimes\ldots it's not. but\ldots more often than not, yeah. 
like right now\ldots it doesn't feel like a bad idea.}
{\textbf{Genuine + Open. He names genuine uncertainty before he names the 
present moment. The admission that it sometimes fails is not a vulnerability 
strategy --- it is the honest limit of what he knows. She goes still. 
``I don't know yet if it's a good idea either\ldots but it's\ldots not a bad 
one so far.'' First voluntary softening without being prompted toward it. 
She has stopped assessing. She has begun feeling something out.}}

\speaker{Her}{going still; then}
{I don't know yet if it's a good idea either\ldots but it's\ldots not a bad 
one so far.}
{First voluntary softening without being prompted toward it. 
She has stopped assessing. She has begun feeling something out.}

\thinrule

\speaker{Her}{after learning he had been listening to a flamenco piece before 
he sat; slight tilt of head}
{\ldots depends. is this one of those moments where you're trying to impress 
me, or you actually just want to share it?}
{She is checking origin again --- not hostile, but precise. She wants to know 
if what she is receiving is performance or presence.}

\speaker{Him}{a bit surprised; not offended}
{you asked me what I was doing, right?}
{The redirect is not defensive. It is accurate. She catches it: 
``okay, yeah. that's on me.'' The piece plays.}

\thinrule

\speakeraction{Him}{Duel to the Death plays; around the percussive section 
her foot begins tapping without her noticing}
{When it ends she offers genuine criticism --- the opening felt expected --- 
and then asks whether that was intentional. When he names the title, she 
replays it with the context and arrives at the structure herself. 
She has begun completing meaning he did not deliver.}

\thinrule

\speaker{Him}{glances her way}
{didn't find anyone who inspired those\ldots sounds\ldots in a while. 
\textit{looks away}}
{\textbf{Genuine + Open. She tests it for convenience: ``that sounds like 
you're dependent on something outside you.'' He does not defend. 
He corrects gently.}}

\speaker{Him}{gently; the tenderness noticeable if you are paying attention}
{it's not that\ldots they're not there. it's just\ldots better when they 
are there for someone.}
{She reconsiders. ``okay\ldots that's different from what I thought you meant.'' 
Then: ``still sounds a little dangerous though. you don't really control where 
that ends up, do you?'' He says nothing.}

\speakeraction{Him}{says nothing; nods slowly, horizontally --- 
as if she finally saw something}
{\textbf{Silence as Genuine + Open at its most compressed: the nod is the 
fragment, meaning entirely open. She fills it herself --- and the filling costs 
her something. She is no longer observing him. She is thinking about herself.}}

\thinrule

\speaker{Him}{looks down; gaze softens; smile vanishes slightly as memories 
surface; then replaced by a bright one --- no lingering sadness, only 
acceptance; then back to her}
{I accept.}
{\textbf{Cognition Fracture, low register. The brief dip --- real memories 
surfacing --- and the clean return. She notices the contrast: ``you don't seem 
like someone it's been easy for. but you also don't seem like you're pretending 
it was. that's\ldots better than most.'' She has stopped checking whether he is 
genuine. She has concluded that he is.}}

\speaker{Her}{watching the contrast; something shifting in her}
{you don't seem like someone it's been easy for. but you also don't seem like 
you're pretending it was. that's\ldots better than most.}
{She is no longer running any audit. She has arrived at a conclusion.}

\thinrule

\speaker{Him}{looks at her more directly; smile still there, playful --- 
but eyes tender}
{I don't pretend.}
{}

\speaker{Her}{quiet exhale; doesn't look away immediately}
{\ldots yeah. I can tell. \textit{brief pause} it's a little disarming, 
actually. most people hide behind something. you're just\ldots here. 
\textit{glances down, then back up, softer} I'm still deciding if that's 
a good thing.}
{She is naming what she has observed across the whole arc. The observation 
costs her something --- she is not delivering a judgment. She is sharing 
an experience.}

\speaker{Him}{accepting look; playful and unbudged}
{yeah\ldots you are.}
{\textbf{Genuine + Closed. The two words do not attempt to resolve her 
indecision. They leave it exactly where it sits. She notices: ``you're oddly 
patient\ldots most people would've tried to steer this somewhere by now. 
you're just letting it be what it is\ldots that's new.'' 
She is no longer receiving the atmosphere. She is beginning to name it. 
Synchrony has arrived.}}

\thinrule

\speaker{Her}{something warmer entering her voice}
{you're oddly patient\ldots most people would've tried to steer this 
somewhere by now. you're just letting it be what it is\ldots that's new.}
{She is no longer receiving the atmosphere. She is beginning to name it. 
Synchrony has arrived.}

\speaker{Him}{names that the unhurried quality feels freeing}
{}
{She agrees --- then adds: ``but also a bit\ldots exposing.'' A genuine 
fragment from her side. She is now producing her own incompletion. 
When he says ``me too'' --- admitting the exposure is mutual --- 
she exhales visibly. ``good to know you're not just\ldots immune to it 
or something.'' The bilateral field is forming.}

\thinrule

\speaker{Him}{leans in slightly then pulls back --- 
as if catching himself before closing the distance}
{it\ldots felt more real. kinder.}
{}

\speaker{Her}{slight tilt of head}
{\ldots kinder? than what?}
{}

\speaker{Him}{pausing; thinking; releasing the thought before it is fully shaped}
{the alternatives. rushing\ldots as if\ldots as if the one I'm with\ldots 
mattered less than what I wanted.}
{She goes very quiet. ``it's a weird feeling when you realize someone's more 
focused on getting somewhere than\ldots being with you.'' She is no longer 
describing a general observation. She is describing something she has felt. 
The framework produced the condition for her to say something true. 
It did not prompt her to say it.}

\thinrule

\speakeraction{Him}{shifts slightly closer; not much --- but she notices}
{}

\speaker{Her}{doesn't move away; holds his gaze, steady but not tense}
{\ldots I noticed that. I'm\ldots still here. \textit{brief pause} just don't 
make it feel like you're trying to\ldots change the pace suddenly. 
this was working.}
{She names the boundary directly. The contact had moved before she was ready. 
She said so plainly.}

\speaker{Him}{looks at her; not backing away; tender --- 
acknowledging her boundary; then relaxes back into the seat}
{I hear you. I won't.}
{\textbf{He did not retreat. He did not over-apologise. He acknowledged and 
settled. She exhales --- tension she had not fully shown releasing. 
``thanks for\ldots not making that weird. you're kinda good at this\ldots 
but not in an annoying way. it's\ldots balanced.'' The boundary was met with 
steadiness, not management. She found nothing to pull back from.}}

\thinrule

\speaker{Him}{eyebrows raising playfully}
{good? oh my.}
{\textbf{Cognition Fracture in miniature. The mock-vanity escaped before it 
could be managed. Something genuine slipped through. She catches it immediately, 
suppresses a smile, and leans back slightly. ``don't get carried away\ldots 
I said not annoying. that's a very specific compliment.'' Warmth has entered 
her teasing. The guard is no longer present in any meaningful sense.}}

\speaker{Her}{suppressing a smile; leaning back slightly}
{don't get carried away\ldots I said not annoying. that's a very specific 
compliment.}
{Warmth has entered her teasing. The guard is no longer present in any 
meaningful sense.}

\thinrule

\speakeraction{Him and Her}{what follows is the most concentrated passage of 
co-authorship in any of these transcripts; neither person is managing the 
interaction; meaning accumulates in the space between them without either 
directing it there}
{He observes he already got what he wanted. She presses: \textit{what did 
you get?}}

\speaker{Him}{looks down at the space between them; then back to her}
{this\ldots it's\ldots just right.}
{\textbf{Genuine + Open. ``Just right'' is anchored but unresolved --- right 
how, right for what? She fills it: ``this is\ldots easy. not in a boring way 
--- just\ldots not forced.'' She has supplied the definition. The Completion 
Bond has formed. She is no longer receiving the atmosphere. She is 
co-authoring it.}}

\speaker{Her}{settling the definition herself}
{this is\ldots easy. not in a boring way --- just\ldots not forced.}
{She has completed meaning he did not deliver. The Completion Bond is formed.}

\thinrule

\speaker{Her}{studying him; something genuinely curious underneath it}
{I can't tell which parts of you are instinct and which are practiced. 
you're\ldots curated. somehow.}
{She is not accusing. She is trying to locate what she is actually receiving. 
There is a real edge of vulnerability underneath the question --- she wants 
to know if what she is experiencing is real.}

\speaker{Him}{something slipping out before the decision to share it}
{\textit{it slips out} flustered. \textit{face changes --- genuine mix of 
horror and amusement} I --- I said that out loud\ldots didn't I.}
{\textbf{Cognition Fracture, high register. The word escaped before the 
decision to share it. She stares for a moment. Then it lands. 
``you did\ldots flustered, huh?\ldots that's the first unfiltered thing 
you've said all evening. I was starting to think you didn't do that.''}}

\speaker{Him}{visible blush; nods slowly and awkwardly; a gentleness to it}
{yeah yeah.}
{}

\speaker{Her}{tilting head; watching him recover}
{\ldots okay, that's actually kind of endearing. \textit{brief pause} see, 
that feels different. less\ldots composed. I like that more than the 
perfectly measured version of you.}
{\textbf{First Slip confirmed. She has offered something from her own interior 
--- a preference, a genuine admission --- without being asked. The bilateral 
field is now fully established.}}

\thinrule

\speakeraction{Him and Her}{the final arc moves through a sustained silence 
neither person fills; through the name of his grandmother and what she gave 
him; through her own quiet reciprocal disclosure about someone who made things 
feel less heavy; the Completion Bond has long since formed; what remains is 
simply presence}
{}

\speakeraction{Him}{fingers rest near hers on the wall; not touching --- 
clearly beginning something; meaning entirely open}
{\textbf{Physical Generative Incompletion. The hand is a fragment. 
She had named the boundary earlier when the pace shifted too fast. 
Now the distance closes without either person asking it to. 
It closes because neither is asking it to stay.}}

\speakeraction{Her}{notices; her hand shifts on the bench --- not touching, 
not preserving the distance either; just acknowledging}
{}

\speaker{Her}{not a question; shifts her fingers slightly --- closer, still 
not crossing that last bit; holds his gaze; something warmer settling}
{\ldots you felt that too. you didn't rush it. that matters.}
{\textbf{Bilateral Moment. She names his restraint as the thing that made 
the contact possible. She is co-authoring the meaning of the gesture --- 
not receiving it, but finishing it. The Completion Bond in its most 
complete expression.}}

\thinrule

\speakeraction{Him and Her}{the contact arrives gradually: a light brush; 
then his fingers tracing a slow circle on hers; then a deliberate graze; 
she mirrors it; neither person has pressed for this}
{\textbf{She had named the boundary when the pace moved too fast. 
What arrives now is not the same movement. It is something that formed 
slowly enough that she chose it at every stage. That is the difference. 
She was never directed here. She arrived.}}

\speaker{Her}{writes the ending}
{\ldots I'll meet you in it.}
{\textbf{She writes the ending. Not because anything directed her there. 
Because the atmosphere was genuine enough that she chose to go there herself.}}

\goldrule

\begin{calloutbox}
\textbf{Summary --- Case Study II}\\[0.6em]
The exchange opened under conditions of active, sustained scrutiny. 
She was guarded, observant, and checking throughout --- for polish, 
for vagueness, for urgency, for construction. She found none of it, 
not because it was hidden, but because it was not there. No Cognition 
Fracture was planned. The ``flustered'' slip was involuntary --- something 
real became too present to contain. The blush that followed was not managed. 
The grandmother disclosure emerged naturally from her asking what he had been 
doing before he sat; it was not positioned as vulnerability. Four confirmed 
Fractures occurred across the arc: the brief memory surfacing and clean return 
when accepting pain; the ``flustered'' slip; the visible blush held without 
recovery; and the fingers twitching toward hers before the decision not to move. 
All were received without management. Physical Generative Incompletion --- 
fingers near hers, the traced circle, the deliberate graze --- operated 
identically to its verbal form: clearly begun, meaning entirely open, 
she completed it by not pulling away and then by moving toward it. 
She had named the boundary when the pace moved too fast earlier. 
What arrived at the end was not the same movement. It formed slowly enough 
that she chose it at every stage. The final gesture --- ``I'll meet you in it'' 
--- was produced by her, not directed toward her. That is the test. 
She wrote the ending because the atmosphere earned it.
\end{calloutbox}