The following exchanges are drawn from live-simulated interactions conducted under 
controlled conditions. Each participant was given a fully-fleshed persona with no 
advance disclosure of the framework. All three simulations were blind --- the subject 
adapted in real time without prior knowledge of the persona's personality type or the 
structural principles being applied.

Annotations mark structural moments: where Generative Incompletion appeared, 
where Cognition Fracture occurred, where the Completion Bond formed, and where the 
framework failed or recovered.

The purpose is not to present ideal execution. It is to show the mechanism 
operating in actual dialogue --- including misreads, recoveries, and the moments 
where something real escaped before it could be managed.

The three exchanges are deliberately varied in condition. 
\hyperref[subsec:case_study_1]{Case Study I} opens with no resistance and no agenda --- the 
question it answers is what the framework looks like when presence is the only thing operating. 
\hyperref[subsec:case_study_2]{Case Study II} opens with her initiating contact and follows an 
arc built on sustained honesty. 
\hyperref[subsec:case_study_3]{Case Study III} operates in a different register entirely, 
demonstrating the mechanism under sustained pressure and explicit audit.

\newpage
% ── Case Study I ─────────────────────────────────────────────────────────────
\subsection*{Case Study I --- The Caf\'{e}}\label{subsec:case_study_1}
\input{CaseStudies/case_study_1.tex}

\newpage
% ── Case Study II ─────────────────────────────────────────────────────────────
\subsection*{Case Study II --- The Park}\label{subsec:case_study_2}
\input{CaseStudies/case_study_2.tex}
\newpage
% ── Case Study III ────────────────────────────────────────────────────────────
\subsection*{Case Study III --- The Unhurried One}\label{subsec:case_study_3}
\input{CaseStudies/case_study_3.tex}